---
title: "Temperature Converter"
output: html_document
---
**Name: Linqi Yang**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### I. Overview
This is a temperature converter that takes temperature values in Celsius as inputs and returns temperature values in Fahrenheit as outputs.

### II. Calculations in the Tmperature Converter 
Celcius (input) * 9/5 + 32 = Fahrenheit (output)  

### III. How to Use the Temperature Converter 
- Move the slider on the left panel to input a temperature value in Celcius.  
- A corresponding temperature value in Fahrenheit will display on the right panel. 

### IV. Examples  
- 0 Celcius = 32 Fahrenheit  
- 100 Celcius = 212 Fahrenheit

### V. Note
The temperature converter only takes in integer values from 0 Celcius **(freezing point)** to 100 Celcius **(boiling point)**.

### VI. Appendix (Code)
**ui**
```{r, eval=F}
library(shiny)
shinyUI(fluidPage(
    titlePanel("Celsius to Fahrenheit"),
    sidebarLayout(
        sidebarPanel(
            h1("Celsius"),
            sliderInput("slider2", "Move the Slider!", 0, 100, 0)
        ),
        mainPanel(
            h3("Fahrenheit"),
            textOutput("text1")
        )
    )
))
```

**server**
```{r, eval=F}
library(shiny)
shinyServer(function(input, output) {
    output$text1 = renderText(input$slider2 *9/5 + 32)
})
```