
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Introduction
<div class="red2">
This is a temperature converter **(produced using shiny package in RStudio)** that takes temperature values in Celsius as inputs and returns temperature values in Fahrenheit as outputs.  

## The Temperature Converter
### **Simple & Quick to Use**
1. Move the slider on the left panel to input a temperature value in Celcius.  
2. A corresponding temperature value in Fahrenheit will display on the right panel. 

### **Calculations behind the Scene**
Celcius (input) * 9/5 + 32 = Fahrenheit (output)  

## How it works
- **0 Celcius = 32 Fahrenheit**  
```{r, comment = ""}
temp1_c <- 0
(temp1_f <- temp1_c * 9/5 + 32)
```

- **100 Celcius = 212 Fahrenheit**  
```{r, comment = ""}
temp2_c <- 100
(temp2_f <- temp2_c * 9/5 + 32)
```

## Conclusions
### **Note**  
The temperature converter only takes in integer values from 0 Celcius **(freezing point)** to 100 Celcius **(boiling point)**.

### **Implications**
This simple temperature converter can be expanded with a larger scale and also for convertions of currency, length and etc.
